Joint training of classification model and similarity model for low-resource text classification in chatbot

### 2020-09-09 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex

  Given   a   data   point   $x_{i}$  with  class  label  $y_{i}$  from  dataset
  $\mathcal{D}$, we take the final hidden state $h_{i}$ of the first token [CLS]
  encoded  by  RoBERTa  as the representation for the whole sequence of $x_{i}$.
  Then  a linear layer is followed to output probabilistic distribution of class
  labels,  $softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$,  where $W^C$ and $b^C$
  are  trainable  parameters.  Then, the loss in stage 1 classification model is
  shown in Equ. \ref{eq:classification loss},

  \begin{equation}
    \begin{aligned}
      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
      \label{eq:classification loss}
    \end{aligned}
  \end{equation}

@@

  Suppose  we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of
  $N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
  single  class label from a class label set of $C$ classes in total. If we want
  to             generate            sentence            pair            dataset
  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
  generated  from two user history queries \footnote{For simplicty, we use query
  to denote a user's question or a response.} and $l_{j}\in\{0, 1\}$ denotes the
  similarity label, see Equ. \ref{eq:similarity label},
  \begin{align}
    l_{j}=
    \begin{cases} \label{eq:similarity label}
      0 & y_{x}\neq y_{x'}\\
      1 & y_{x}=y_{x'}
    \end{cases}
  \end{align}
  directly  from  original  dataset $\mathcal{D}$ without any sampling strategy,
  then  $\mathcal{D'}$  will have $M=N^2$ data points of sentence pairs. That is
  time-consuming  for  the  training  in stage 2 since we often have hundreds of
  class  labels  under task-specific chatbot scenario. Though we may only have a
  few data points for a single class label, $M$ is still prohibitively large.

@@

  The  first step is \emph{positive sentence pair sampling}. During the training
  process,  we first make sure the ground truth class label $y_{i}$
  for  $x_{i}$  is  within  the  candidate  class  label  set $\mathcal{C'}$. If
  $y_{i}\notin  \mathcal{C'}$,  we manually add $y_{i}$ into $\mathcal{C'}$
  by  replacing  $c'_{K}$  with  $y_{i}$,  since $c'_{K}$ is the least promising
  candidate  label  according  to the auxiliary model in stage 1. Afterwards, we
  will randomly sample $P$ sentences $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the
  same  class  label  as  $y_{i}$  from dataset $\mathcal{D}$ to form the set of
  sentence  pairs  with positive label $\mathcal{P'}_{i}=\{[(x_{i}, x'_{0}), 1],
  [(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},  x'_{P}), 1]\}$, where $P$ is also a
  hyperparameter  set  to control  the number of sentences we should
  sample from each class.

  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
  that  the  sentence  pairs  with  negative  label  grouped by user input query
  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
  are  strong  adversarial  negative  samples for sentence-pair similarity model
  that  can  help  enhance  the training speed and performance. According to the
  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{0}),
  0], [(x_{i}, x'_{1}), 0], ..., [(x_{i}, x'_{P\cdot (K-1)}), 0]\}$

@@

  Due  to  the  fact that sentence pairs within the same class is much fewer than
  that from  different  classes,  the  dataset  $\mathcal{D'}$  is
  quite imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
  to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
  \ref{eq:similarity loss}.

  \begin{equation}
    \begin{aligned}
      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
      \label{eq:similarity loss}
    \end{aligned}
  \end{equation}

@@

  With  the  average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also
  generate   a   top-K   class   label   $l^{K}_i\in   [1,\dots,K]$   for   each
  ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
  task is shown in Equ. \ref{eq:top-k classification loss}. In Equ. \ref{eq: pos
  top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
  $\xi_{i,l^{K}_{i}}^{K,pos}$  and  $\xi_{i,l^{K}_{i}}^{K,neg}$  encourage  high
  level  of  similarity  and  low  level  of dissimilarity for prediction of the
  correct label $l^{K}_i$ within the top-K candidate classes.

  \begin{align}
    \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
    \label{eq:top-k classification loss}
  \end{align}
  where

@@

  Finally,  the  overall  loss  function for multi-task learning in stage 2 is
  shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively.
  which  are
  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.

@@

  \begin{table*}
    \begin{centering}
      \scalebox{0.9}{
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} & \textbf{\#Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 1942 & 8 & class sampling\tabularnewline
        \hline 
        HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
      \end{tabular}
      }
    \par
    \end{centering}
    \caption{Statistics for all datasets and few shot settings\footnote{All
    settings of four public datasets would be released to github soon}.}

@@

  There  are 3 tasks in total during the training process of joint SFC, shown in
  Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
  the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
  $\alpha_S$,   $\alpha_K$   and   $\alpha_C$   represent the  weights  for  task  1,
  sentence-pair  similarity,  task  2,  top-K classification and task 3, general
  single sentence classification respectively.
  \begin{align}
    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
    \label{eq:joint_SFC_loss}
  \end{align}

  \subsection{Datasets}
  Our experiments aim to study the short text classification in the low-resource
  environment  popular  in  the  task-specific conversional chatbot application.
  Hence we choose and configure set datasets to serve this study. Different from
  the  datasets from other short text classification research, such as semantics
  classification  with  very  limited  semantics labels and several sentences as
  input,   the   datasets  adopted  in  our  experiments  are  typically  having
  comparatively  large  number  of  class labels, ranging from several dozens to
  hundreds,  and  each  class  label  is  associated  with  a handful of labeled
  queries,  and  each  query  is  usually  one  sentence. Table \ref{tbe:dataset
  statistic} displays their statistics.

@@

          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{Full} & \textbf{Full}\tabularnewline

@@

          RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.9584$} & \multirow{2}*{$0.9621$} & \multirow{2}*{$0.9733$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.9227$} & \multirow{2}*{$0.9313$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7493$} & \multirow{2}*{$0.7678$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline

@@

        F-scores on five task-specific dataset for text classification in chatbot under low resource. For ITG, we keep the full dataset. For Amazon-670k, we randomly sampled 250 classes with training sample numbers within 5-15 samples per class. For CLINC150, BANKING77, HWU64, we set up various few-shot settings (5/10/15/20/30/50 samples per class) while keeping the test set to be fixed. The highest scores for each data setting are marked in bold.

@@

@@

  \subsection{System description}
  We choose three kinds of system to construct our baselines.

@@

    \item   \emph{Non-pretrained   model  based  classification  system},  which
    consists  of  a popular CNN based TextCNN \cite{kim2014convolutional}, and a
    recently  proposed label-embedding based LEAM (todo: reference and its label
    setting). Empircally,
    a  non-pretrained  model  based  system  are  not  performing  as  well as a
    pretrained  models  based,  if  both is applicable in some task. Our listing
    these  non-pretrained model based systems here is to provide a comprehensive
    performance comparison on our datasets.

@@

      \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline 
        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
        \hline
      \end{tabular}
      \par
    \end{centering}
    \caption{
      We  show the performance of SFC from different settings of hyperparameters
      for  $K$,  the candidate class number, and $P$, the sample number for each
      class.
    }

    \label{tbe:table3}
  \end{table*}

  \subsection{Result Analysis}

  Table  \ref{tbe:table2} presents all results on the five datasets model set-up
  in  detail.  The performance of each model is measured in F-score on the fixed
  test  set  for  each  dataset.  Overall,  two-stage  SFC systems show moderate
  improvements  over  all  baseline systems. This observation gives us a general
  idea  that  classification  model  and  similarity  model can actually provide
  complementary  information  to  each  other,  and  combining them together can
  enhance the overall capability based on richer extracted semantic information.
  Furthermore, we also studied the performance among all the variants of SFCs on
  different data settings to explore the benefits brought by multi-task training
  and the joint-model structure.

  \subsubsection*{Which SFC variant performs best?} 
  First, we compare the four  SFC  variants to analyze the improvement
  brought  by  multi-task  and  joint-model  structure.

@@

@@

  \subsubsection*{How does joint SFC interact with the classfication in stage
  1?}
  {todo: content}

  \subsubsection*{How does SFC perform with different  training  data  size} 
  We analyze the
  overall  improvement  trend  of  SFC under various few-shot settings.

@@

  \subsubsection*{How is joint SFC related to the label  embedding based  LEAM?}
  LEAM performs consistently better than TextCNN by a large margin in all
  datasets. TextCNN is practically efficiently in task-specific chat
  applications, and LEAM shows its power in modeling labeling information.

>>>>

  Given   a   data   point   $x_{i}$  with  class  label  $y_{i}$  from  dataset
  $\mathcal{D}$, we take the final hidden state $h_{i}$ of the first token [CLS]
  encoded  by  RoBERTa  as the representation for the whole sequence of $x_{i}$.
  Then  a linear layer is followed to output probabilistic distribution of class
  labels,  $softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$,  where $W^C$ and $b^C$
  are  trainable  parameters.  Then, the loss in stage 1 classification model is
  shown in Equ. \ref{eq:classification_loss},

  \begin{equation}
    \begin{aligned}
      \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
      \label{eq:classification_loss}
    \end{aligned}
  \end{equation}

@@

  Suppose  we have a training dataset $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$ of
  $N$  data  points,  in  which $x_{i}$ is the user input query and $y_{i}$ is a
  single  class label from a class label set of $C$ classes in total. We 
  generate            a sentence            pair            dataset
  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$ from $\mathcal{D}$,   where   $(x,   x')_{j}$  is
  a pair of two history queries \footnote{For simplicty, we use query
  to denote a user's question or a response.}, and $l_{j}\in\{0, 1\}$ denotes the
  similarity label that the ones from the same class label are considered
  similar. The size of $\mathcal{D'}$  would be up to $O(N^2)$ if no any
  sampling strategy is used.  This is quite time-consuming  for the  training
  in stage 2 because $N$ can be several hundreds or thousands even under 
  few shot setting in task-specific chatbot scenario.

@@

  The  first step is \emph{positive sentence pair sampling}. During the training
  process,  we  first make sure the ground truth class label $y_{i}$ for $x_{i}$
  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
  \mathcal{C'}$,  we  manually  add  $y_{i}$  into  $\mathcal{C'}$  by replacing
  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
  sample  $P$ sentences $\{x'_{1}, \dots, x'_{P}\}$ with the same class label as
  $y_{i}$  from  dataset  $\mathcal{D}$  to  form the set of sentence pairs with
  positive  label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{1}),  1],  \dots,  [(x_{i},
  x'_{P}),  1]\}$,  where $P$ is also a hyperparameter set to control the number
  of sentences we should sample from each class.

  The  second  step  is  \emph{negative sentence pair sampling}: As for negative
  sentence  pairs,  we will also randomly sample $P$ sentences for each class in
  the negative candidate class label set $\mathcal{C'}\backslash \{y_{i}\}$. The
  class  labels  in  $\mathcal{C'}\backslash  \{y_{i}\}$  are  the  set  of most
  confusing  class  labels comparing to the ground truth ${y_{i}}$, so we assume
  that  the  sentence  pairs  with  negative  label  grouped by user input query
  $x_{i}$  and sentences with class labels in $\mathcal{C'}\backslash \{y_{i}\}$
  are  strong  adversarial  negative  samples for sentence-pair similarity model
  that  can  help  enhance  the training speed and performance. According to the
  same  method  as  positive  sentence  pair  sampling, we can obtain the set of
  sentence  pairs  with  negative label as $\mathcal{N'}_{i}=\{[(x_{i}, x'_{1}),
  0], ..., [(x_{i}, x'_{P\cdot K}), 0]\}$

@@

  Due  to  the  fact that sentence pairs within the same class is much fewer than
  that from  different  classes,  the  dataset  $\mathcal{D'}$  is
  quite imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
  to  the  loss  to eliminate the bias brought by data imbalance, shown in Equ.
  \ref{eq:similarity_loss}.

  \begin{equation}
    \begin{aligned}
      \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
      \label{eq:similarity_loss}
    \end{aligned}
  \end{equation}

@@

  With  the  average pooling result ${\xi}^{K,pos}$ and ${\xi}^{K,neg}$, we also
  generate   a   top-K   class   label   $l^{K}_i\in   [1,\dots,K]$   for   each
  ${\xi}^{K,pos}_{i}$ and ${\xi}^{K,neg}_{i}$. The loss for top-K classification
  task is shown in Equ. \ref{eq:top-k_classification_loss}. In Equ. \ref{eq: pos
  top-k   loss}   and   Equ.   \ref{eq:   neg   top-k   loss},  the  first  term
  $\xi_{i,l^{K}_{i}}^{K,pos}$  and  $\xi_{i,l^{K}_{i}}^{K,neg}$  encourage  high
  level  of  similarity  and  low  level  of dissimilarity for prediction of the
  correct label $l^{K}_i$ within the top-K candidate classes.

  \begin{align}
    \mathcal{L}^{K} = \frac{1}{N}\sum_{i=1}^{N}(\mathcal{L}^{K,pos}_{i} - \mathcal{L}^{K,neg}_{i})
    \label{eq:top-k_classification_loss}
  \end{align}
  where

@@

  Finally,  the  overall  loss  function for multi-task learning in stage 2 is
  shown in Equ. \ref{eq:two-stage_SFC_loss}. The training objective of stage 2 is
  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively.

@@

  \begin{table*}
    \begin{centering}
      \scalebox{0.9}{
        \begin{tabular}{|c|c|c|c|c|c|}
          \hline 
          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
          \hline 
          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
          \hline 
          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
          \hline 
          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
        \end{tabular}
      }
      \par
    \end{centering}
    \caption{Statistics for all datasets and few shot settings\footnote{All
    settings of four public datasets would be released to github soon}.}

@@

@@

          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$
          & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ &
          $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ &
          $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ &
          $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{3-fold} &
          \textbf{3-fold}\tabularnewline

@@

          RoBERTa-large & \multirow{2}*{$\textbf{0.8974i}$} &
          \multirow{2}*{$\textbf{0.9372}$} & \multirow{2}*{$\textbf{0.9508}$} &
          \multirow{2}*{$\textbf{0.9584}$} & \multirow{2}*{$\textbf{0.9621}$} & 
          \multirow{2}*{$\textbf{0.9733}$} & \multirow{2}*{$\textbf{0.7690}$} & 
          \multirow{2}*{$\textbf{0.8728}$} & \multirow{2}*{$\textbf{0.8966}$} & 
          \multirow{2}*{$\textbf{0.9099}$} & \multirow{2}*{$i\textbf{0.9227}$} & 
          \multirow{2}*{$\textbf{0.9313}$} & \multirow{2}*{$\textbf{0.6044}$} & 
          \multirow{2}*{$\textbf{0.7002}$} & \multirow{2}*{$\textbf{0.7129}$} & 
          \multirow{2}*{$\textbf{0.7436}$} & \multirow{2}*{$\textbf{0.7493}$} & 
          \multirow{2}*{$\textbf{0.7678}$} & \multirow{2}*{$\textbf{0.7990}$} & 
          \multirow{2}*{$\textbf{0.7156}$}\tabularnewline

@@

      F-scores  on  five  task-specific  datasets text classification in chatbot
      under low resource. For ITG, we keep the full dataset. For Amazon-670k, we
      randomly  sampled  250  classes  with  training sample numbers within 5-15
      samples  per  class.  For  CLINC150,  BANKING77,  HWU64, we set up various
      few-shot  settings  (5/10/15/20/30/50 samples per class) while keeping the
      test  set to be fixed. The highest scores for each data setting are marked
      in bold.

@@

  There  are 3 tasks in total during the training process of joint SFC, shown in
  Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
  the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
  $\alpha_S$,  $\alpha_K$  and  $\alpha_C$  represent  the  weights  for  task 1
  sentence-pair  similarity  in  Equ.  \ref{eq:similarity_loss},  task  2  top-K
  classification  in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
  single       sentence       classification      respectively      in      Equ.
  \ref{eq:classification_loss}.

  \begin{align}
    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
    \label{eq:joint_SFC_loss}
  \end{align}

  \subsection{Datasets}
  Our experiments aim to study the short text classification in the low-resource
  environment  popular  in  the  task-specific conversional chatbot application.
  Hence we choose and configure set datasets to serve this study. Different from
  the  datasets from other short text classification research, such as semantics
  classification  with  very  limited  semantics labels and relatively longer
  input,   the   datasets  adopted  in  our  experiments  are  typically  having
  comparatively  large  number  of  class labels, ranging from several dozens to
  hundreds,  and  each  class  label  is  associated  with  a handful of labeled
  queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
  statistic} displays their statistics.

@@

  \subsection{Baselines}
  We choose three kinds of system to construct our baselines.

@@

    \item   \emph{Non-pretrained   model  based  classification  system},  which
    consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a
    label-embedding based LEAM \cite{wang2018joint}. Regarding TextCNN, the
    model is based on output from RoBERTa tokenization, and the kernels are set
    as 1, 2, 3, 4, 5. Regarding LEAM, a literal class label is required, which
    is available only in HWU64, CLINC150, BANKING77. Thus, for other two
    datasets, we have to use its class number instead.  Empircally,
    a  non-pretrained  model  based  system  are  not  performing  as  well as a
    pretrained  models  based,  if  both is applicable in some task. Our listing
    these  non-pretrained model based systems here is to provide a comprehensive
    performance comparison on our datasets.

@@

  \subsection{Result Analysis}
  All results in F-score (todo: reference) on the five datasets with different models and configurations are
  showed in Table  \ref{tbe:table2}.

  The performance of each model is measured in F-score on the fixed
  test  set  for  each  dataset.  
  Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
  improvements  over  corresponding baselines, and joint SFC deliver more
  significant and consistent improvements over the best baseline, RoBERTa based
  classification. In following content, we dive into more details.

  \subsubsection*{Is multi-task and joint training working?} 
  First, we compare the four  SFC  variants to analyze the improvement
  brought  by  multi-task  and  joint-model  structure.

@@

      \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline 
        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
        \hline
      \end{tabular}
      \par
    \end{centering}
    \caption{
      We  show the performances of SFC from different settings of
      hyperparameters, $K$  denoting the candidate class number from stage 1,
      $P$ denoting the number of sampled sententence pair in stage 2. 
    }
    \label{tbe:table3}
  \end{table*}

@@

  \subsubsection*{Does joint SFC improve the classfication in stage 1?}
  {todo: content}

  \subsubsection*{How does training sample size influence SFC?} 
  We analyze the
  overall  improvement  trend  of  SFC under various few-shot settings.

@@

  \subsubsection*{How does joint SFC relate to the label  embedding based  LEAM?}
  LEAM performs consistently better than TextCNN by a large margin in all
  datasets. TextCNN is practically efficiently in task-specific chat
  applications, and LEAM shows its power in modeling labeling information.
